Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-02 Thesis/chapter/061-results-emma.tex
MSE for t=1,2,3,4, pre-opt too

It is interesting that measured 
%%% MAIN INFLUENCE 
%Even without considering the large maximum of $T_{cal}$,

@@

\begin{align}
%
    \label{eq:emma-phd1}
    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
    \label{eq:emma-G1}
    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
    \label{eq:emma-layr1}
    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
    \label{eq:emma-vcal1}
    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
%
    \label{eq:emma-phd2}
    \hat{\rho}_2 &= 47\\
    \label{eq:emma-G2}
    \hat{\gamma}_2 &= 0.23\\
    \label{eq:emma-layr2}
    \hat{\lambda}_2 &= 7.3\\
    \label{eq:emma-vcal2}
    \hat{v}_{cal,2} &= 10\\
%
    \label{eq:emma-phd3}
    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-G3}
    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-layr3}
    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-vcal3}
    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
%
    \label{eq:emma-phd4}
    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-G4}
    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-layr4}
    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-vcal4}
    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
\end{align}
%\fi
%what was the best result? For each particle there is best and global best.

>>>>

For each generation the \gls{mse} was calculated such that only samples were used which were available at that time. 
It is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
The high \gls{mse} can be explained because the prediction function is only a constant at $t=2$. 
Appart from the second generation the \gls{mse} falls over time, which might be attributed to overfitting.
The \gls{mse} for each generation was calculated between predicted values for pre-optimisation samples to check for overfitting, 
but the the error sank with each generation (except for the second gen): 102, 118, 58, 50, respectively for $t=1,2,3,4$.

It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
the combined \gls{mse} for $t=4$ is lower. 
%%% MAIN INFLUENCE 
%Even without considering the large maximum of $T_{cal}$,

@@

\begin{align}
%
%    \label{eq:emma-phd1}
%    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
%    \label{eq:emma-G1}
%    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-layr1}
%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-vcal1}
%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
%
%    \label{eq:emma-phd2}
%    \hat{\rho}_2 &= 47\\
%    \label{eq:emma-G2}
%    \hat{\gamma}_2 &= 0.23\\
%    \label{eq:emma-layr2}
%    \hat{\lambda}_2 &= 7.3\\
%    \label{eq:emma-vcal2}
%    \hat{v}_{cal,2} &= 10\\
%
    \label{eq:emma-phd3}
    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-G3}
    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-layr3}
    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-vcal3}
    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
%
    \label{eq:emma-phd4}
    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-G4}
    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-layr4}
    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-vcal4}
    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
\end{align}
%\fi
%what was the best result? For each particle there is best and global best.
